\documentclass{article}
\usepackage{amsmath,,amsthm}
\usepackage{graphicx}
\usepackage{float}
\usepackage{tfrupee}
\usepackage{enumitem}
\begin{document}

\providecommand{\myvec}







\section*{\centering SECTION-A}
\subsection*{\centering Question numbers 1 to 6 carry 1 mark each}
\begin{enumerate}
	\item If $A$=$\left[
			\begin{matrix}
			\cos\alpha&\sin\alpha\\
			-\sin\alpha&\cos\alpha\\
			\end{matrix}
	        	\right]$,find $\alpha$ satisfying $0\textless\alpha\textless\frac{\pi}{2}$when $A+A^T$=$\sqrt{2}$$I_{2}$;where $A^T$ is transpose of $A$.
	\item For what values of k,the system of linear equations\\
		$x+y+z=2$\\
		$2x+y-z=3$\\
		$3x+2y+kz=4$\\
		has a unique solution?
	
\item If $A$ is a $3\times 3$ matrix and $|3A|=k|A|$, then write the value of $k$.
\item Write the sum of intercepts cut of by the plane $\vec{r}.(2\hat{i}+\hat{j}-\hat{k})-5=0$ on the three axes

\item Find $\lambda$ and $\mu$ if\\
	$(\hat{i}+3\hat{j}+9\hat{k})$$\cdot$$(3\hat{i}-\lambda\hat{j}+\mu\hat{k})$=$0$
	
\item If $\vec{a}$=$4\hat{i}-\hat{j}+\hat{k}$ and $\vec{b}=2\hat{i}-2\hat{j}+\hat{k}$,then find a unit vector parallel vecter $\vec{a}=\vec{b}$


	\section*{\centering SECTION-B}
		\subsection*{\centering Question numbers 7 to 19 carry 4 marks	each.}
		
	\item Slove for $x:\tan^{-1}(x-1)+\tan^{-1} x+\tan^{-1}(x+1)=\tan^{-1}3x$\\
		\subsection*{\centering OR}
		Prove that $\tan^{-1}(\frac{6x-8x^3}{1-12x^2})-\tan^{-1}(\frac{4x}{1-4x^2})$=$\tan^{-1}2x;|2x|\textless\frac{1}{\sqrt{3}}.$
	\item A typist charges \rupee $145$ for typing 10 english and 3 hindi pages while charges 3 english and 10 hindi pages are \rupee 180 Using matrices, find the charges of typing one English and one Hindi page separately. However typist charged only 2 per page from a poor student Shyam for 5 Hindi pages. How much less was charged from this poor boy? Which values are reflected in this problem?

	\item  If  f(x) = $\begin{cases}
\frac{\sin(a+1)x + 2\sin x}{x}, & x < 0 \\
   2, & x = 0 \\
   \frac{\sqrt{1+bx} - 1}{x}, & x > 0
    \end{cases}$
	\text{ is continuous at $x=0$, then find the values of a and b}.
	
\item If $x\cos{a+y}=\cos{y}$ then prove that $\frac{dy}{dx}$=$[\frac{\cos^2(a+y)}{\sin a}]$.\\
		hence show that $\sin a\frac{d^{2}y}{dx^2}+\sin 2(a+y)\frac{dy}{dx}=0$

      \subsection*{\centering OR}

		Find $\frac{dy}{dx}$ if $y:wq=\sin^{-1}[\frac{6x-4\sqrt{1-4x^2}}{5}]$
	\item Find the equation of tangents to the curve $y = x ^ 3 + 2x - 4$ which perpendicular to line $x + 14y + 3 = 0$
	
	\item Find : $\int\frac{(2x-5)e^{2x}}{(2x-3)^3}$dx.

		\subsection*{\centering OR}

		Find : $\int\frac{x^2+x+1}{(x^{2}+1)(x+2)}$dx.

	\item Evaluate : $\int_{-2}^{2}\frac{x^2}{1+5^x}dx$.

	\item Find : $\int{(x+3)\sqrt{3-4x-x^2}}dx$
	
	\item Find the particuler solution for differential equation : $\frac{dy}{dx}=-\frac{x+y\cos x}{1+\sin x}$ given that $y=1$ when $x=0$
	
	\item Find the particular solution of thedifferential equation $2ye^\frac{x}{y}dx+(y-2xe^\frac{x}{y})dy=0$\\given that $x=0$ when $y=1$.
	
	\item Show that the four points $A(4, 5, 1) B(0, -1, -1) C(3, 9, 4)$and $D(-4, 4, 4)$ are coplanar.
    
	\item Find the coordinates of the foot of perpendicular drawn from the point $A(-1, 8, 4)$ to the line joining the points $B(0, 1, 3)$ and $C(2,3,1)$. Hence find the image of the point $A$ in the line $BC$.
    
	\item A bag $X$ contains $4$ white balls and $2$ black balls, while another bag $Y$ contains $3$ white balls and $3$ black balls. Two balls are drawn (without replacement) at random from one of the bags and were found to be one white and one black. Find the probability that the balls were drawn from bag $Y$.
	
		\subsection*{\centering OR}

     $A$ and $B$ throw a pair of dice alternately, till one of them gets a total of $10$ and wins the game. Find their respective probabilities of winning, if $A$ starts first.

         \section*{\centering SECTION-C}
	\subsection*{\centering Question numbers 20 to 26 carry 6 marks  each.}	

\item Three numbers are selected at random (without replacement) from first six positive integers. Let $X$ denote the largest of the three numbers obtained. Find the probability distribution of $X$. Also, find the mean and variance of the distribution.

\item $A=R \times R$ and * be a binary operation on A defined by $(a,b)*(c,d)=(a+c,b+d)$\\
	Show that is commutative and associative. Find the identity element for * on $A$. Also find the inverse of every element $(a, b) \epsilon A$.

\item Prove that $y=\frac{4\sin{\theta}}{2+\cos{\theta}}-\theta$ is an increasing function of $\theta$ on $[0,\frac{\pi}{2}]$
	\subsection *{\centering OR}
	
	Shoe that semi-vertical angle of cone of maximum volume and given slant hight is $\cos^{-1}(\frac{1}{\sqrt{3}})$
\item Using the methode of integration. Find the area of the trianguler region whose vecters are ($(2, -2)(4, 3)$ and$(1, 2)$

\item Find the euation of the plane which contains the line of intersection of the plane \\
	$\vec{r}\cdot(\hat{i}-2\hat{j}+3\hat{k})-4=0$\\
	$\vec{r}\cdot(-2\hat{i}+\hat{j}+\hat{k})+5=0$\\
	and whose intercept on x-axis is equal tothat of on y-axis.


	\item A retired person wants to invest an amount of \rupee $50,000$. His broker recommends investing in two type of bonds $'A'$ and $'B'$ yielding $10\%$ and $9\%$ return respectively on the invested amount. He decides to invest at least\rupee $20,000$ in bond $'A'$ and at least \rupee $10,000$ in bond $'B'$. He also wants to invest at least as much in bond $'A'$ as in bond $'B'$. Solve this linear programming problem graphically to maximise his returns.

	\item Using properties of determinant prove that \\
		$\left|
		\begin{matrix}
			(x+y)^{2} & zx &  zy\\
			zx & (z+y)^{2} & xy\\
			zy & xy & (z+x)^{2}\\
		\end{matrix}
		\right|$
		=$2xyz(x+y+z)^{3}$
           \subsection*{\centering  OR}

   \item  If $A=\left(
	   \begin{matrix}
		   1 & 0 & 2 \\
		   0  & 2 & 1 \\
		   2 & 0 & 3 \\

	   \end{matrix}
	   \right)$.and $A^3-6A^2+7A+kI_3=0$  find $K$.




\end{enumerate}
\end{document}


